---
title: "Get_WGS84_Coordinates"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Get_WGS84_Coordinates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

Usually, it's not convenient to get the real latlon geocode [(wgs84, which is standard for GPS)](https://earth-info.nga.mil/GandG/update/index.php?dir=wgs84&action=wgs84) of a location with Chinese characters, especially for large amount of locations.

Here is a method to retrieve the coordinates of massive locations by [amap api](https://lbs.amap.com/dev/), and convert to the real GPS coordinates, which is easy for future geography usage.

# Install package

With the following code, you can install this package.
```{r install, eval=FALSE}
remotes::install_github("jimrpy/getcoords")
```

There are some other packages required, `dplyr`, `tidyr`, `purrr`, `stringr`, `jsonlite`, `tibble`, if not installed before, install now with `install.packages(c("pkg1", "pkg2",...))`.

## Get a amap API key

This function depends on the webservice of [amap api](https://lbs.amap.com/dev/), a valid key is a must before using it. For registered user, the permission is 6,000 locations/day; for validated personal developer, the permission is 300,000 locations/day. 

Use `usethis::edit_r_environ()` to edit the R environment file. For example  
`key_amap_tmp = "Yourkey"`  

**Restart** `R`, check whether the key is installed in `Rstudio` Console  
`Sys.getenv("key_amap_tmp")`
If the result matches your key chain, all is ok... 

Congratulations!!! Go ahead...

## Load package
```{r setup}
library(getcoords)
library(magrittr)
library(DT)
library(tidyr)
library(dplyr)
library(purrr)
library(leaflet)
```

# Example locations
Here are 60 random company locations with Chinese characters in a `data.frame`, you can handle as many locations as you `amap key` permission.
```{r example-raw, echo=FALSE}
set.seed(1234)
file = system.file("extdata", "example_locations.csv", package = "getcoords")
df = read.csv(file = file)
df= df %>%
 sample_n(size = 60) 
```

```{r table-raw-data}
DT::datatable(data = df)
```

# Get the real GPS coordinates
This is a real scenario, hard work for conventional methods to get the real GPS coordinates. With this package, you can use `geocode` function to finish in minutes.

```{r example wgs84}
df.new <- df %>% 
  dplyr::mutate(latlon = map(.x = location, .f = ~geocode(.x))) %>% 
  tidyr::unnest(latlon) %>% 
  dplyr::select(-location)

df.new %>% 
  DT::datatable(data = .,  caption = "example locations with WGS84 coordinates")
```

The coordinates may not be all correct, the reason is that the location you input is not standard. The good location should like such pattern `province county township village`.


# Interactive map with locations

Now you can plot a attractive map, enjoy it!!!
```{r map, fig.width=7.3}
leaflet() %>% 
  addProviderTiles(provider = providers$OpenStreetMap) %>% 
  addCircleMarkers(data = df.new, 
                   lng = ~lon, 
                   lat = ~lat, 
                   radius = 0.5, 
                   color = "red",
                   popup = ~loc.input
                  )
```
